A Massive Molecular Gas Reservoir in the $z$\,=\,2.221 Type-2 Quasar Host Galaxy SMM\,J0939+8315 lensed by the Radio Galaxy 3C220.3

### 2015-12-07 mod1/response.txt

We thank the referee for providing constructive comments to improve this manuscipt. We have addressed all the concerns raised by the referee and details can be found in the revised version, please see attached. A brief description on how we incoprated the changes can be found below. 
=====================

Major comments:
- There is already a lensing model in H14 (a paper the authors refer to numerous times) and it is unclear why they redid the lensing model (they use the same SMA data as H14 but a different code). If the derived model is significantly different from H14 then this should be highlighted otherwise the lens modeling section isn't necessary in this paper.
> We moved the lens mass and consistent results into table 1 and its caption, and removed details of the lens model / shortened the section. However, we retained this section in this paper as we provide the best-fit parameters that were not reported in Haas14 and since we use the inferred half-light radius later in the analysis.

- section 4.3 is way too wordy and can be cut down to a few paragraphs and a table summarizing these key values (already given in Table 4). These are all standard calculations and you can refer to CW14 for the equations rather than repeating them here.
> We removed standard equations from the manuscript, combined the sections reporting SFE and SFR into one, and trimmed a few sentences.

- You should also summarize the evidence for the AGN in this SMG (maybe when you mention this in the intro) so the reader doesn't have to read H14.
> We rephrased the introduction to show more clearly the evidence of an AGN.

- [a further concern/question about Table 4 is whether all the same assumptions such as excitation, alpha_co, etc. were made for the other SMGs otherwise the comparisons are meaningless]
> We added notes in the caption below Table 4 to recap the assumptions used in deriving these quantities.
=============================

- The SMG is thought to harbor a luminous AGN. In that case, the LIR will certainly have a contribution from the AGN that should be accounted for otherwise the SFR will be overestimated: see e.g. Coppin+2010, Kirkpatrick+2012, Magdis+2013, Kirkpatrick+2014. Please correct LIR for the AGN emission prior to estimating SFR and include an AGN component in the SED fitting. 
>In our analysis, we fit SED models to the rest-frame FIR, which has been found to have AGN negligible contributions to IR luminosities - Pope+08 report that AGN contributions to the bolometric IR luminosity is at most 30%. Since we do not have MIR data (for just the background SMG, as postive K blueward of dust peak), we didn't fit an AGN component. Including an additional component, and thus free parameters to the SED model will be over-fitted due to the limited amount of data at hand. Instead our SED model includes a power-law to the blue side of the dust peak, which accounts for the MIR excess and allows us to estimate the IR luminosity (Kirkpatrick+15, Riechers+13, Johnson+13, Casey+12).

or should I change it to FIR --> SFR
> In our analysis, we fit SED models to the rest-frame FIR, which has been found to have negligible AGN contribution to rest-frame FIR (≥ 60µm; Carilli+05, Netzer+07, Mullaney+11, Harrison+15). We derived the SFR and other corresponding properties using the L_FIR, (45-122.5), which SF-driven dust emission.
> --> then change SFR using L_FIR instead of L_IR

@@

- Section 5: why do the authors cherry-pick these 2 SMGs to make comparisons? there are many other sources that could be chosen with a range of properties. A comparison to these 2 SMGs is not useful at all given the diversity in this population (e.g. the sentence "This demonstrates the large ..." is not true when comparing only 3 objects). I suggest comparing to the general properties observed for SMGs (as summarized in CW14 or Casey+14) which will be more useful in placing this object in the context of the SMG population. 
> added columns to table referencing the properties of the population from a review. We picked out two lensed gravitaitonally lensed SMGs to demonstrate the power? extreme cases of SMGs which are intrinsically sit at the bright and faint ends.

- the discussion/conclusions should focus on what is new from this paper and not what is already presented in H14. E.g. the last sentence about this SMG transitioning from starburst to QSO phase. How is that conclusion made or strengthened with this new data?
> SFR and massive gas reservoir, coupled with the low depletion time of gas --> its short phase in the proposed evolutionary link

# Minor comments:
- the depletion time seems short compared to other SMGs which are ~100Myr although maybe it is consistent with other SMGs with AGN in them.
> Taken into account one of the comments listed above, we added literature reference to Table 4, and the depletion time scale is consistent with other SMGs.
> Greve05: 40-100 Myr

============================
**DONE**
- section headings in 3 are strange. Remove the words "New results" since this is obvious and a requirement for publication. Also remove subheading or second line in heading 3.2.
> we have removed "New results" in the subject headings

### 2015-12-08 mod1/manuscript/ms.tex
replaced properties with FIR derived, combined SFR SFRSD sections; need to work on Tab.4 and conclusion

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
{\bf  Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
%, this is consistent the value reported by H14 within the errors. 
and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
All best-fit
parameters are listed in Table~\ref{tab:lensParam}. {\bf DR: Note changes to Tab 1}
%The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
%the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
\input{table_lensParams}

@@

\subsubsection{Molecular Gas Mass} \label{sec:gas}
While the ground state CO transition line traces the cold molecular gas in the ISM
\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
 ground state transition line is redshifted to lower frequencies that can only be observed with traditional radio telescopes
 \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the $M$(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
 conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
%Prior to observations of the ground state CO transition line in SMGs, it had been assumed that the molecular gas in the
%  ISM traceable by CO lines was thermalized owing to their high star formation rates \citep[\eg][]{Greve05a, Coppin08a}.
{\bf Recent observations of the ground state CO transition line in SMGs have demonstrated that these galaxies can be sub-thermally excited regardless of their high SFRs
   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. 
 Moreover, observational results of SMGs with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements have shown that the
   brightness temperature ratio is commonly found to be $R_\textrm{31}<$ 0.8 \citep
   {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}.} In contrast, similar observations in high-redshift quasar hosts suggest that the ratio
   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}. In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements. \par
{\bf Here, we derive the molecular gas mass
assuming thermalized excitation of CO, as SMM\,J0939 is
postulated to be hosting a type-2 quasar (H14).}
We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
\citep[\eg][]{Solomon05a}. This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU; hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification. We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}.
This results in a gas-to-dust
ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24. 
%We note that as outlined in the previous section, a factor of $\sim$\,2 uncertainty arises from the dust mass estimate. 
This is in good agreement  with the
values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.

\subsubsection{{\bf Star Formation Rate \& Star Formation Efficiency}}
We derive the {\bf SFR} assuming that the dominant IR heating source is due to young and massive stars, and ignoring a contribution from the
dust-enshrouded AGN.
Using the \citet{Kennicutt98a} relation and assuming a \citet{Chabrier03a}
stellar initial mass (IMF) function\footnote{The SFR would be SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
\odot$ yr\pmOne\ if we were to use only the FIR luminosity.},
we derive a SFR$_\textrm{IR}$ of 874\,$\pm$\,122 $\Msun$\,\,yr\pmOne, employing the lensing-corrected total IR luminosity.
The starburst in SMM\,J0939 can be maintained at its
current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR.
This corresponds to $\tau_\textrm{depl}$\,=\,31\,$\pm$\,5 Myr, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.

%\subsubsection{Star Formation Efficiency}
The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency. 
{\bf We compute this ratio using the IR
and CO luminosities ($L_\textrm{IR}$/\Lp). The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
IMF. }This, however, assumes that differential lensing between the {\bf CO and IR} emission is negligible.
The resulting ratio is SFE$_\textrm{IR}$\,=\,256\,$\pm$\,41\,\,\Lsun\,(\LpU)$^{-1}$, this is comparable
to those found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.

\subsubsection{Dynamical Mass}
Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized. With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}, with the FWHM of the \CO line profile and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO. 
We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.  We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}. 
{\bf In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO measurements and 
the small sample of SMGs with spatially resolved \rot{1}{0} observations show that the cool gas are even more extended \citep{Ivison11a, Riechers11c, Hodge13a}. For dust-emitting region, \citet{Simpson15a} report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
% Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
 }

\subsubsection{Star Formation and Gas Surface Densities}
{\bf We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
radius \citep[\eg][]{Genzel10a, Harrison15a}, yielding 
%To compute surface densities, we divide half the inferred SFR and gas mass by the area subtended by the half-light
%radius, resulting in 
$\Sigma_\textrm{SF}$ = 175.20 \Msun~yr\pmOne~kpc$^{-2}$ and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively. 
These results are in good agreement with values typical for SMGs \citep{Tacconi08a}. }
The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$\,=\,9.3\,($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
galaxies
out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.

@@

The detection of CO in SMM\,J0939
implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
molecular gas reservoir that fuels the star formation activity taking place at a rate of $\sim$\,874 \Msun~yr\pmOne. If the star forming activity continues at the current rate, the gas reservoir will be depleted within $\lesssim$~31 Myr,
which is consistent with the short timescales found in other SMGs \citep{Greve05a}. The derived intrinsic properties of SMM\,J0939 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a 
population of high-redshift galaxies that build up the bulk of stellar mass in present-day galaxies, thus play an important role
in galaxy formation and evolution \citep[\eg ][]{Dickinson03a}.

We investigate variations within the SMG population by comparing SMM\,J0939 with two other exceptionally submm-bright,
strongly-lensed SMGs
found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The properties
of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as
the
longest gas depletion timescale (\ie is the most long-lived), the overall gas and dust properties of SMM\,J0939 fall between those of HLSW-01 and the
cosmic
Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250 \micron, the lensing magnification
varies by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the
three, this
intrinsically fainter, and less gas-rich SMG appears notably bright
at 250\,\micron, while its CO line and IR luminosities are lower than those of most SMGs studied to date.
This demonstrates
the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.
While lensing can probe sources
of various intrinsic properties, we find that SMM\,J0939 is representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date
\citep[\eg ][]{Greve05a,Tacconi08a}.

@@

 %%% EDIT %%%%
We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
based on the excellent agreement found between their {\bf gas and dust} properties (see \S~\ref{sec:SEDBg} and \S~\ref{sec:gas}).
{\bf In the evolutionary BLAH BLAH}
This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.

>>>>

The resulting best-fit model as shown in Figure\,\,\ref{fig:lens} shows no significant bowls in the residual
image, and the knots (lensed emission) in the observed SMA data are well-reassembled with the best-fit model.
{\bf  Our best-fit model yields a magnification
factor of $\mu_\textrm{L}$ = 10.13\,$\pm$\,1.38
%, this is consistent the value reported by H14 within the errors. 
and a half-light radius of 0\farcs11 $\pm$ 0\farcs03, corresponding to a spatial extent of $\sim$0.9 kpc.} 
All best-fit
parameters are listed in Table~\ref{tab:lensParam}. {\bf DR: Please Note changes to Tab 1}
%The Einstein radii associated with the best-fit model for the two lenses are $\theta_{E}$ = 1\farcs22\,$\pm$\,0\farcs01 (8.75 kpc at $z$\,=\,0.685) and $\theta_{E}$ = 0\farcs75\,$\pm$\,0\farcs02 (5.34\,\,kpc at $z$\,=\,0.685), and
%the corresponding masses within the Einstein radii are $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(4.86\,$\pm$\,0.08)\,$\times$\,10$^{11}$\,\,\Msun\ and $M(\theta$\,\,$<$\,\,$\theta_\textrm{E})$\,=\,(1.82\,$\pm$\,0.07)\,$\times$\,10$^{11}$\,\,\Msun, respectively.
\input{table_lensParams}

@@

\subsubsection{Molecular Gas Mass} \label{sec:gas}
While the ground state CO transition line traces the cold molecular gas in the ISM
\citep*[\eg][]{Wilson70a,Downes98a}, transition lines of higher rotational states ($J$ $>$ 1) are frequently observed in high-redshift sources as the
 ground state transition line is redshifted to lower frequencies that can only be observed with traditional radio telescopes
 \citep{Carilli13a}. Consequently, assumptions on the CO excitation conditions are required to derive the molecular gas mass using the $M$(H$_\textrm{2}$)-to-$L^{\prime}_\textrm{CO}$
 conversion factor ($\alpha_\mathrm{CO}$) when extrapolating from higher-$J$ CO lines. \par
{\bf Recent observations of the ground state CO transition line in SMGs have demonstrated that these galaxies can be sub-thermally excited regardless of their high SFRs
   \citep{Harris10a,Riechers11c,Riechers11d,Ivison11a}. 
 Moreover, observational results of SMGs with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements have shown that the
   brightness temperature ratio is commonly found to be $R_\textrm{31}<$ 0.8 \citep
   {Harris10a,Carilli10a,Swinbank2010a,Ivison10d,Ivison11a,Riechers11d}.} In contrast, similar observations in high-redshift quasar hosts suggest that the ratio
   is $R_\textrm{31}$\,$\sim$\,1 \citep{Riechers06a, Riechers11a}. In the case of high-redshift type-2 quasars, \citet{Riechers11a} report a brightness temperature ratio of $R_\textrm{31}$ = 1.00\,$\pm$\,0.10 for IRAS F10214+4724 (hereafter F10214), which is currently the only known type-2 quasar with both \CO and CO($J$\,=\,1\,\rarr\,0) line measurements. \par
{\bf Here, we derive the molecular gas mass
assuming thermalized excitation of CO, as SMM\,J0939 is
postulated to be hosting a type-2 quasar (H14).}
We calculate the CO($J$\,=\,1\rarr\,0) line luminosity using a standard relation
\citep[\eg][]{Solomon05a}. This corresponds to \Lp = (3.42\,$\pm$\,0.71)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU; hence the inferred total molecular gas mass is $M_\textrm{gas}$ = (2.74\,$\pm$\,0.57)\,$\times$\,\,10$^{10}$\,\Msun\, after correcting for lensing magnification. We assumed a conversion factor of $\alpha_\textrm{CO}$ = 0.8\,\,\Msun\,(\LpU)\pmOne\ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep[\eg][]{Tacconi06a,Tacconi08a,Bothwell13a}.
This results in a gas-to-dust
ratio of $f_\textrm{gas-dust}$\,=\,$M_\textrm{gas}/M_\textrm{dust}$\,=\,55\,$\pm$\,24. 
This is in good agreement  with the
values found in other SMGs \citep{Coppin08a,Micha10a,Riechers11c}.

\subsubsection{{\bf Star Formation Rate \& Star Formation Efficiency}}
{\bf We derive the SFR using the lensing-corrected FIR luminosity assuming 
that the dominant heating source of cold-dust is young and massive stars and ignoring a contribution from the
dust-enshrouded AGN.}
Using the \citet{Kennicutt98a} relation and {\bf adopting} a \citet{Chabrier03a}
stellar initial mass (IMF) function, {\bf we find a
SFR$_\textrm{FIR}$\,=\,526\,$\pm$\,73 $M_
\odot$ yr\pmOne.}
The starburst in SMM\,J0939 can be maintained at its
current rate for a time that can be approximated by the gas depletion timescale, $\tau_\textrm{depl}$\,=\,$M_\textrm{gas}$/SFR{\bf , which assumes no replenishment of gas and feedbacks.}
This corresponds to {\bf $\tau_\textrm{depl}$\,=\,52\,$\pm$\,8 Myr}, which is in good agreement with those found in other SMGs \citep[\eg][]{Greve05a}.

The SFR per unit mass of molecular gas is commonly taken as a
measure of the star formation efficiency. 
{\bf We compute this ratio using the {\bf FIR}
and CO luminosities {\bf ($L_\textrm{FIR}$/\Lp)}. The derived SFE is therefore independent of the magnification factor, the CO luminosity to gas mass conversion factor ($\alpha_\textrm{CO}$), and the
IMF. }This, however, assumes that differential lensing between the {\bf CO and FIR} emission is negligible.
The resulting ratio is {\bf SFE$_\textrm{FIR}$\,=\,154\,$\pm$\,25\,\,\Lsun\,(\LpU)$^{-1}$}, this is comparable
to those found in ``typical" SMGs \citep{Greve05a,Tacconi06a,Riechers11c}.

{\bf We compute the surface densities by dividing half the SFR and gas mass by the area subtended by the half-light
radius \citep[\eg][]{Genzel10a, Harrison15a}, yielding 
$\Sigma_\textrm{SF}$ = 106  \Msun~yr\pmOne~kpc$^{-2}$} and $\Sigma_\textrm{gas}$ = 5.48\,$\times$\,10$^9$ \Msun~kpc$^{-2}$, respectively. 
These results are in good agreement with values typical for SMGs {\bf \citep{Tacconi06a, Hodge15a}. }  % compared using their conversion
The inferred surface densities of SMM\,J0939 follow a universal Schmidt-Kennicutt relation between the star formation rate
surface density and the molecular gas surface density: $\Sigma_\textrm{SF}$ = 9.3\,($\pm$\,2)\,$\times$\,10$^{-5}$ ($M_\textrm{gas}$/2$\pi R_\textrm{1/2}^2)^{1.71(\pm\,0.05)}$, which was derived using a sample consisting of local star-forming galaxies and high-redshift
galaxies
out to $z$\,$\sim$\,2.5, and assuming a Chabrier IMF \citep{B07a}.

\subsubsection{Dynamical Mass}
Based on our \CO line measurement, we estimate the dynamical mass of SMM\,J0939 assuming that the molecular gas is virialized. With this assumption, we use an isotropic virial estimator \citep[\eg][]{Engel10a}, with the FWHM of the \CO line profile and the half-light radius from our lens model for $R_\textrm{eff}$, assuming that the dust emission traces the same emitting region as the CO. 
We find a dynamical mass of $M_\textrm{dyn}$ = (7.84\,$\pm$\,2.84)\,$\times$\,10$^{10}$\,\Msun, and a gas-to-dynamical mass fraction of $f_\textrm{gas-to-dyn}$ = 0.35\,$\pm$\,0.14, consistent with those of other SMGs \citep{Tacconi06a}.  We note that a derived dynamical mass based on this assumption is likely to be biased towards low values, as the CO-emitting region {\bf that traces the cool gas} can be spatially more extended than the dust emitting region due to the low dust optical depth at larger radii \citep[\eg][]{Tacconi06a, Riechers11c,Riechers11d,Ivison11a}. 
{\bf This has been supported by recent observations. In particular, \citet{Tacconi06a} report a median FWHM size of 4.1\,$\pm$\,1.6 kpc based on \CO line measurements of their sample, whereas studies with spatially resolved \rot{1}{0} observations have additionally demonstrated that the cool gas regions are even more extended (R$_{\rm eff} \sim$ 7 kpc;  \citealt{Ivison11a}, see also \citealt{Riechers11c, Hodge13a}). 
For the physical size of dust-emitting regions, \citet{Simpson15a} recently report a spatial extent of 2.4 kpc in a sample of 52 SMGs.
% Adopting a physical size of 4.1 kpc, we find a dynamical mass of 3.7\,$\times$\,10$^{11}$\,\Msun.
 }

@@

The detection of CO in SMM\,J0939
implies a CO luminosity of \Lp\ = (3.4\,$\pm$\,0.7)\,$\times$\,10$^{10}$\,(10.1/$\mu_\textrm{L}$) \LpU, suggesting the presence of a massive
molecular gas reservoir that fuels the star formation activity taking place at a rate of {\bf $\sim$\,526 \Msun~yr\pmOne}. If the star forming activity continues at the current rate, the gas reservoir will be depleted within {\bf $\lesssim$~52 Myr,}
which is consistent with the short timescales found in other SMGs \citep{Greve05a}. The derived intrinsic properties of SMM\,J0939 are evident of ongoing rapid star formation; this is in good agreement with the current conjecture that SMGs are a 
population of high-redshift galaxies that build up the bulk of stellar mass in present-day galaxies, thus play an important role
in galaxy formation and evolution \citep[\eg ][]{Dickinson03a}.

{\bf We
compare our findings for SMM\,J0939
 with two other exceptionally submm-bright,}
strongly-lensed SMGs
found at similar redshifts --- HLSW-01 and the cosmic Eyelash, both of which have been studied in great detail. The properties
of these galaxies are listed in Table~\ref{tab:comapreSMG}. While the cosmic Eyelash has the least amount of molecular gas, as well as
the
longest gas depletion timescale (\ie is the most long-lived), the overall gas and dust properties of SMM\,J0939 fall between those of HLSW-01 and the
cosmic
Eyelash. Such distinction is likely a result of our selection bias: while these sources appear similarly bright at 250 \micron, the lensing magnification
varies by a factor of $\sim$\,3. In particular, with the cosmic Eyelash having the highest lensing magnification among the
three, this
intrinsically fainter, and less gas-rich SMG appears notably bright
at 250\,\micron, while its CO line and IR luminosities are lower than those of most SMGs studied to date.
{\bf This demonstrates BLAH BLAH
the large variations in gas mass, dust mass, and star forming activity within the population at $z$\,$\sim$\,2$-$3, which is discernible with the aid of gravitational lensing.}
While lensing can probe sources
of various intrinsic properties, we find that SMM\,J0939 is representative of the SMG population, with its intrinsic CO line luminosity, IR luminosity, gas mass,
dust mass, SFR, SFE, depletion timescale, and gas mass fraction comparable to those found in ``typical" SMGs studied to date
\citep[\eg ][]{Greve05a,Tacconi08a}.

@@

 %%% EDIT %%%%
BLAH BLAH
We conclude this paper by noting that SMM\,J0939 is a faithful representation of both high-redshift type-2 quasars and SMGs,
based on the excellent agreement found between their {\bf gas and dust} properties (see \S~\ref{sec:SEDBg} and \S~\ref{sec:gas}).
{\bf In the proposed evolutionary paradigm, BLAH}
This is supportive of the proposed evolutionary phase model \citep[\eg][]{Sanders88,Coppin08a,Simpson12a}, whereby SMM\,J0939 is transitioning from its star-bursting phase to the unobscured quasar phase.
